---
title: "imageTCGA: A Shiny application to explore the TCGA Diagnostic Image Database"
author:
- name: Ilaria Billato
  affiliation: [
    "Department of Biology, University of Padova"
  ]
- name: Marcel Ramos
  affiliation: >
    CUNY Graduate School of Public Health and Health Policy, New York, NY USA
- name: Vincent J. Carey
  affiliation: > 
    Channing Lab, Brigham and Womens Hospital,
    Harvard University, Boston, MA USA
- name: Sean Davis
  affiliation: > 
    Channing Lab, Brigham and Womens Hospital,
    Harvard University, Boston, MA USA
- name: Sehyun Oh
  affiliation: > 
    CUNY Graduate School of Public Health and Health Policy, New York, NY USA
- name: Levi Waldron
  affiliation: > 
    CUNY Graduate School of Public Health and Health Policy, New York, NY USA
- name: Davide Risso
  affiliation: > 
    Department of Statistical Sciences, University of Padova
- name: Chiara Romualdi
  affiliation: > 
    Department of Biology, University of Padova
- name: ADD OTHERS
  affiliation: > 
    Department of Biology, University of Padova
package: imageTCGA
output:
  BiocStyle::html_document:
    toc: false
vignette: >
  %\VignetteIndexEntry{imageTCGA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# imageTCGA

`imageTCGA` is an R package designed to provide an interactive Shiny application for exploring the TCGA Diagnostic Image Database. This application allows users to filter and visualize clinical data, geographic distribution, and other relevant statistics related to TCGA diagnostic images.


# Installation

```{r,eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("imageTCGA")
```

## Setup

Load the package.

```{r,eval=FALSE}
# load imageTCGA
library(imageTCGA)
```

## Run the shiny App
After installing the package, you can run the Shiny application by executing the following command in R:

```{r,eval=FALSE}
imageTCGA::imageTCGA()
```

This command will launch the interactive application in your default web browser.

# Session Info

```{r}
sessionInfo()
```
